---
title: "A Gental Intro to Rcpp"
author: "Dan Murphy"
date: "Thursday, February 05, 2015"
output: html_document
---

This R Markdown document reproduces the example code in 
'Chapter 1: A Gental Introduction to Rcpp' of
*Seamless R and C++ Integration with Rcpp*
stored in the folder
"/SkyDrive/Trinostics/Rcpp Book".

## 1.2 A First Example

Finonacci sequence 

$$ 
F_n = F_{n-1} + F_{n-2} 
$$

with these two initial conditions

$$ 
F_0 = 0, F_1 = 1 
$$

```{r}
fibR <- function(n) {
  if (n == 0) return(0)
  if (n == 1) return(1)
  return(fibR(n - 1) + fibR(n - 2))
}
fibR(0:9)
sapply(0:9, fibR)
```

#### Implement the recursion in C++

We need a pure C/C++ function as the generated function 
will have a random identifier at the C++ level 
preventing us from direct recursive calls.

```{r}
incltxt <- '
int fibonacci(const int x) {
  if (x == 0) return(0);
  if (x == 1) return(1);
return fibonacci(x - 1) + fibonacci(x - 2);
}'
```

Now use the snippet above as well as one argument conversion
in as well as out to forvide Fibonacci numbers via C++:

```{r}
library(inline)
fibRcpp <- cxxfunction(signature(xs = "int"),
                       plugin = "Rcpp",
                       incl = incltxt,
                       body = '
  int x = Rcpp::as<int>(xs);
  return Rcpp::wrap(fibonacci(x));
')
# fibRcpp(0:9) # Error in eval(...): expecting a single value
sapply(0:9, fibRcpp)
getwd()
```

#### 1.2.5 Using Rcpp Attributes

Created a new file in RStudio, a new C++ file with the code on p. 11
of the book. 
Named it fibonacci.cpp.
Then

```{r}
sourceCpp("fibonacci.cpp")
fibonacci(20)
```

#### 1.2.7 A Second C++ Solution

```{r}
## memoization using C++
mincltxt <- '
#include <algorithm>
#include <vector>
#include <stdexcept>
#include <cmath>
#include <iostream>

class Fib {
public:
  Fib(unsigned int n = 1000) {
    memo.resize(n); // reserve n elements
    std::fill( memo.begin(), memo.end(), NAN ); // set to NaN
    memo[0] = 0.0; // initialize for
    memo[1] = 1.0; // n=0 and n=1
  }
  double fibonacci(int x) {
    if (x < 0) // guard against bad input
      return( (double) NAN );
    if (x >= (int) memo.size())
      throw std::range_error(\"x too large for implementation\");
    if (! ::isnan(memo[x]))
      return(memo[x]); // if exist, reuse values
    // build precomputed value via recursion
    memo[x] = fibonacci(x-2) + fibonacci(x-1);
    return( memo[x] ); // and return
  }
private:
  std::vector< double > memo; // internal memory for precomp.
};
'
```