---
title: "A Gental Intro to Rcpp"
author: "D Eddelbuettel"
date: "Thursday, February 05, 2015"
output: html_document
---

This R Markdown document reproduces the example code in 
'Chapter 1: A Gental Introduction to Rcpp' of
*Seamless R and C++ Integration with Rcpp*
stored in the folder
"/SkyDrive/Trinostics/Rcpp Book".

```{r}
xx <- faithful$eruptions
fit <- density(xx)
plot(fit)
```

```{r}
xx <- faithful$eruptions
fit1 <- density(xx)
fit2 <- replicate(10000, {
  x <- sample(xx, replace = TRUE);
  density(x, from = min(fit1$x), to = max(fit1$x))$y # supplying this
  # from, to range "ensures that the bootstrapped density is estimated 
  # on the same grid of x values as in fit1" (p. 5)
})
fit3 <- apply(fit2, 1, quantile, c(0.025, 0.975))
plot(fit1, ylim = range(fit3))
polygon(c(fit1$x, rev(fit1$x)),
        c(fit3[1,], rev(fit3[2,])),
        col = 'grey', border = F)
lines(fit1)
```
For this data set, the grid contains 512 points
```{r}
length(fit1$x)
```
This is because, via help(density),

> The algorithm used in density.default disperses the mass of the empirical 
distribution function over a regular grid of at least 512 points 

## 1.2 A First Example

Finonacci sequence 
$F_n = F_{n-1} + F_{n-2}$